Effect of quality-adjusted production function inputs

### 2015-07-03 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now including correlograms.

>>>>

%++++++++++++++++++++++++++++++
\section{Correlograms} 
\label{sec:correlograms}
%++++++++++++++++++++++++++++++

This appendix contains correlograms for all models.

%++++++++++++++++++++++++++++++
\subsection{Correlograms for models respecting the cost-share theorem} 
\label{sec:correlograms_CST}
%++++++++++++++++++++++++++++++

In this section we present correlograms for all models that respect the cost-share theorem.

<<Correlograms_CST, echo=FALSE, message=FALSE>>=
leaf_apply(l = modelsCST, class = c("lm", "plm"), f = function(model, name){
  acf(resid(model), main=name)
})
@

%++++++++++++++++++++++++++++++
\subsection{Correlograms for models reject the cost-share theorem} 
\label{sec:correlograms_noCST}
%++++++++++++++++++++++++++++++

In this section we present correlograms for all models that do not adhere to the cost-share theorem.

<<Correlograms_noCST, echo=FALSE, message=FALSE>>=
leaf_apply(l = models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, name){
  acf(resid(model), main=name)
})
